\section{Introduction}
The introduction is traditionally a section which enlightens the reader as to the background of the work.
It can be used to reveal the breadth of the topic via the discussion of research previously undertaken on the subject areas at hand.
This section also aims to provide a reader an understanding of the direction we as the authors have taken to address the null hypothesis presented herein.
So we must provide an interesting question to be addressed, reasoning behind why it has been selected, what has previously been done to address the matter, and then finally what we proposed to do with our work.
This should lead us nicely on to what we did in the method section.
For clarity's sake it is always good to: Tell them what you are gonna tell them. Tell them. Then tell them again. The same rules apply for presentation of material.

Global climate change has spurred a variety of political actions globally; one measure widely adopted has been adoption of more diverse supplies of energy (reducing reliance upon traditional energy vectors such as coal, oil, and gas).
A leading form of renewable energy which has seen strong uptake globally has been wind power, which requires wind turbines; these harness aeolian kinetic energy to rotate generators and generate renewable electricity.
Wind turbines manufactured by this industry have grown substantially since its inception.
Towers have grown taller and blades longer.
Criticism has been levelled at the industry because the vast majority of blades which have been manufactured using thermosetting plastic.
These blades are made of this because of the strengths attained per mass, but the criticism is of the issue of disposal.
The issue of disposal is simply the hatred of landfill. This is somwhat justified.
In the context of carbon cycling this is carbon neutral;locked away carbon is returned to its original place in the ground\dots
Work previously has been focussed on how to recycle these products to avoid the criticism levelled (quote danish scientists at aarhus who made a very clever degradable form of thermoset recently).
This work instead takes a different view on the matter- one of long term carbon cycling.
If thermoset material was made from bio-based resources and optimised to be as strong as traditional resources, then it could be conceivable that this would be carbon negative in a sense.
(ITS NOT THOUGH- MAKE THIS CLEAR- CALL IT THE ENDOGENIC RETURN PRINCIPLE.)
We will therefore focus upon the improvements we could make to a simple class of polyester thermoset called poly(glycerol itaconate citrate).
Perhaps the thesis should feature a standalone section on the endogenic return principle and its groundings- such that it can be spoken of without people getting the impression that I am trying to be carbon negative (people get exceedingly cross if they think I am pulling a fast one on them with respect to carbon neutrality terminology.)
The endogenic return principle is something more fundamental than simply carbon capture storage- CCS is badly defined. This could be a way around this ambiguity, but some clear definitions would have to be generated.
